Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-20 ms.tex
Softened statement about Bayesian Information Criterion.

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{table}
\begin{center}
{\renewcommand{\arraystretch}{1.3}
\renewcommand{\tabcolsep}{0.2cm}
\begin{tabular}{c c}
\hline
\hline
$M_r$ Threshold & $\Delta \mathrm{BIC}$ \\
\hline
-21 & -0.54 \\
-20.5 & 1.33 \\
-20 & 4.56\\
-19.5 & 0.26\\
-19 & 4.37\\
\hline
\end{tabular}
\medskip
\caption{
Change to the Bayesian Information Criterion, $\Delta \mathrm{BIC}$,
after introducing additional parametric freedom to accommodate galaxy
assembly bias. Sign convention is such that positive values favor models including
assembly bias, negative values favor standard HOD models with no assembly bias parameters. Changes in
the Bayesian Information Criterion $\vert \Delta \mathrm{BIC}\vert \ge 5$ strongly favor one model
over another.
}
 }
 \label{table:bic}
 \end{center}
\end{table}
%--------------------------------------------------------------------------------------------------------------------------------

Beyond the fit results, it is also possible to ask whether or not the fits to the data warrant the use of 
additional parameters (in this case, to describe assembly bias). This requires a metric that penalizes the 
use of additional parameters. A commonly used metric is the Bayesian Information Criterion 
\citep[BIC,][]{schwarz78}, defined as 
%
\begin{equation}
\mathrm{BIC} = -2 \mathcal{L}_{\rm max} + k\, \ln N, 
\end{equation}
%
where $\mathcal{L}_{\rm max}$ is the maximum of the likelihood, 
$k$ is the number of paramters in the model and $N$ is the number of 
data points. We compute the change in the BIC, $\Delta$BIC, by subtracting 
the BIC for the analysis with assembly bias from the BIC in the standard analysis 
in which there is no assembly bias. With this convention, $\Delta \mathrm{BIC} > 0$ 
favors assembly bias, suggesting that the data warrant the additional parametric freedom. 
Conversely, $\Delta \mathrm{BIC} < 0$ favors the standard analysis, 
suggesting that the additional freedom in the model does not improve the description of the data 
to a sufficiently great degree to support the added complexity. 
A common convention is to refer to the preference as 
{\em strong} when $\vert \Delta \mathrm{BIC}\vert \ge 5$.

The values of $\Delta$BIC are given in Table~\ref{table:bic}. In the analysis of the $\magr < -21$ sample, 
$\Delta \mathrm{BIC} < 0$, indicating that the additional parameters describing assembly bias are not 
warranted by the data. For all other samples, $\Delta \mathrm{BIC} > 0$, showing a preference for 
the models with assembly bias. The cases that most support the additional complexity 
of the decorated HOD are $\magr < -19$ and $\magr < -20$, for which $\Delta$BIC 
rises nearly to the level of a {\rm strong} preference.

>>>>

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{table}
\begin{center}
{\renewcommand{\arraystretch}{1.3}
\renewcommand{\tabcolsep}{0.2cm}
\begin{tabular}{c c}
\hline
\hline
$M_r$ Threshold & $\Delta \mathrm{BIC}$ \\
\hline
-21 & -0.54 \\
-20.5 & 1.33 \\
-20 & 2.88\\
-19.5 & 0.26\\
-19 & 3.78\\
\hline
\end{tabular}
\medskip
\caption{
Change to the Bayesian Information Criterion, $\Delta \mathrm{BIC}$,
after introducing additional parametric freedom to accommodate galaxy
assembly bias. Sign convention is such that positive values favor models including
assembly bias, negative values favor standard HOD models with no assembly bias parameters. Changes in
the Bayesian Information Criterion $\vert \Delta \mathrm{BIC}\vert \ge 5$ strongly favor one model
over another.
}
 }
 \label{table:bic}
 \end{center}
\end{table}
%--------------------------------------------------------------------------------------------------------------------------------

In addition to fitting model parameters, it is possible to ask whether or not the fits to the data warrant the use of 
additional parameters (in this case, the two parameters used to describe assembly bias). This requires a 
metric that penalizes the use of additional parameters. A commonly-used metric is the 
Bayesian Information Criterion 
\citep[BIC,][]{schwarz78}, defined as 
%
\begin{equation}
\mathrm{BIC} = -2 \mathcal{L}_{\rm max} + k\, \ln N, 
\end{equation}
%
where $\mathcal{L}_{\rm max}$ is the maximum of the likelihood, 
$k$ is the number of paramters in the model and $N$ is the number of 
data points. We compute the change in the BIC, $\Delta$BIC, by subtracting 
the BIC for the analysis with assembly bias from the BIC in the standard analysis 
in which there is no assembly bias. With this convention, $\Delta \mathrm{BIC} > 0$ 
favors assembly bias, suggesting that the data warrant the additional parametric freedom. 
Conversely, $\Delta \mathrm{BIC} < 0$ favors the standard analysis, 
suggesting that the additional freedom in the model does not improve the description of the data 
to a sufficiently great degree to support the added complexity. 
A common convention is to refer to the preference as 
{\em strong} when $\vert \Delta \mathrm{BIC}\vert \ge 5$.

The values of $\Delta$BIC are given in Table~\ref{table:bic}. In the analysis of the $\magr < -21$ sample, 
$\Delta \mathrm{BIC} < 0$, indicating that the additional parameters describing assembly bias are not 
warranted by the data. For all other samples, $\Delta \mathrm{BIC} > 0$, showing a preference for 
the models with assembly bias. The cases that most support the additional complexity 
of the decorated HOD are $\magr < -19$ and $\magr < -20$, for which $\Delta$BIC is 
considerable, but in no case does the $\Delta$BIC rise to the conventional level for {\em strong} 
preference.
